
setwd("C:/Users/avanderlaar/Dropbox/R/Distance")
#setwd("C:/Users/Auriel Fournier/Dropbox/R/Distance")
#load required libraries
library(unmarked)
library(AICcmodavg)
library(ggplot2)
library(reshape2)
library(lattice)
library(sjPlot) 
library(grid)


# 2012 Round 2

#read in the sora observations
sora12 <- read.csv('2012sora.csv', header=T)
sora12 <-  sora12[,colnames(sora12)!=("impounda")]
sora12 <-  sora12[,colnames(sora12)!=("distance")]
#read in the covariate data #organized by impoundment.
cov12 <- read.csv('2012cov.csv', header=T)
#subset just the covariates we need 
cov12 <- cov12[,c("habtype","region","dur","dista","effortm","int","waterd")]

effort12 <- read.csv('effortm12.csv', header=T)
effort12 <-  effort12[,colnames(effort12)!=("X")]
effort12 <-  effort12[,colnames(effort12)!=("impounda")]

date12 <- read.csv('date12.csv', header=T)
date12 <-  date12[,colnames(date12)!=("X")]
date12 <-  date12[,colnames(date12)!=("X1.x")]
date12 <-  date12[,colnames(date12)!=("X1.y")]
date12 <-  date12[,colnames(date12)!=("impounda")]

dates12 <- date12^2

date13 <- read.csv('date13.csv', header=T)
date13 <-  date13[,colnames(date13)!=("X")]
date13 <-  date13[,colnames(date13)!=("X1.x.x")]
date13 <-  date13[,colnames(date13)!=("X1.y.x")]
date13 <-  date13[,colnames(date13)!=("X1.x.y")]
date13 <-  date13[,colnames(date13)!=("X1.y.y")]
date13 <-  date13[,colnames(date13)!=("impounda")]

date12 <-  date12[,colnames(date12)!=("impounda")]

int12 <- read.csv('int12.csv',header=T)
int12 <- int12[,colnames(int12)!=("X")]
int12 <- int12[,colnames(int12)!=("X1.x")]
int12 <- int12[,colnames(int12)!=("X1.y")]
int12 <- int12[,colnames(int12)!=("impounda")]
int13 <- read.csv('int13.csv',header=T)
int13 <- int13[,colnames(int13)!=("X")]
int13 <- int13[,colnames(int13)!=("X1.x")]
int13 <- int13[,colnames(int13)!=("X1.y")]
int13 <- int13[,colnames(int13)!=("impounda")]

waterd12 <- read.csv('waterd12.csv',header=T)
waterd12 <- waterd12[,colnames(waterd12)!=("X")]
waterd12 <- waterd12[,colnames(waterd12)!=("X1.x")]
waterd12 <- waterd12[,colnames(waterd12)!=("X1.y")]
waterd12 <- waterd12[,colnames(waterd12)!=("impounda")]
waterd13 <- read.csv('waterd13.csv',header=T)
waterd13 <- waterd13[,colnames(waterd13)!=("X")]
waterd13 <- waterd13[,colnames(waterd13)!=("X1.x")]
waterd13 <- waterd13[,colnames(waterd13)!=("X1.y")]
waterd13 <- waterd13[,colnames(waterd13)!=("impounda")]


cutpt = as.numeric(c(0,1,2,3,4,5,6,7,8,9,10,11,12)) #the fartherest distance is 12

#Unmarked Data Frame
umf12 = unmarkedFrameGDS(y=sora12, 
                           numPrimary=4,
                           siteCovs = cov12,
                           survey="line", 
                           dist.breaks=cutpt,  
                           unitsIn="m", 
                           tlength=cov12$effortm,
                           yearlySiteCovs=list(date=date12)
                           #dates=dates12, int=int12,waterd=waterd12)
)

##candidate models 
null12 = gdistsamp(lambdaformula = ~1,
                     phiformula = ~1, 
                     pformula = ~1, 
                     data = umf12, keyfun = "hazard",
                     mixture="NB",
                     se = T)

global.d12 = gdistsamp(lambdaformula = ~habtype+dur+dista+region+waterd+int-1, 
                       phiformula = ~date-1,
                       pformula = ~ 1, 
                       data = umf12, 
                       keyfun = "hazard", 
                       mixture="P",
                       se = T)

date12 = gdistsamp(lambdaformula = ~1,
                     phiformula = ~date-1, 
                     pformula = ~1, 
                     data = umf12, keyfun = "hazard",
                     mixture="NB",
                     se = T)

int.d12 = gdistsamp(lambdaformula = ~int-1, 
                  phiformula = ~1, 
                  pformula = ~  1,
                  data = umf12, keyfun = "hazard", mixture="NB",se = T)

waterd.d12 = gdistsamp(lambdaformula = ~waterd-1, 
                  phiformula = ~date-1, 
                  pformula = ~  1,
                  data = umf12, keyfun = "hazard", mixture="NB",se = T)
 
hab.d12 = gdistsamp(lambdaformula = ~habtype-1, 
                   phiformula = ~date-1, 
                   pformula = ~  1,
                   data = umf12, keyfun = "hazard", mixture="NB",se = T)
 
dur.d12 = gdistsamp(lambdaformula = ~dur-1, 
                   phiformula = ~date-1, 
                   pformula = ~  1,
                   data = umf12, keyfun = "hazard", mixture="NB",se = T)

region.d12 = gdistsamp(lambdaformula = ~region-1, 
                  phiformula = ~date-1, 
                  pformula = ~ 1,
                  data = umf12, keyfun = "hazard", mixture="NB",se = T)

dist.d12 = gdistsamp(lambdaformula = ~dista- 1, 
                  phiformula = ~date-1, 
                  pformula = ~  1, 
                  data = umf12, keyfun = "hazard", mixture = "NB", se = T)

hab.int.d12 = gdistsamp(lambdaformula = ~habtype + int - 1, 
                  phiformula = ~date-1, 
                  pformula = ~  1, 
                  data = umf12, keyfun = "hazard", mixture = "NB", se = T)

hab.int.waterd.d12 = gdistsamp(lambdaformula = ~habtype + int + waterd - 1, 
                   phiformula = ~date-1, 
                   pformula = ~  1, 
                   data = umf12, keyfun = "hazard", mixture = "NB", se = T)

hab.waterd.d12 = gdistsamp(lambdaformula = ~habtype + waterd - 1, 
                   phiformula = ~date-1, 
                   pformula = ~  1, 
                   data = umf12, keyfun = "hazard", mixture = "NB", se = T)

hab.dur.d12 = gdistsamp(lambdaformula = ~habtype + dur - 1, 
                   phiformula = ~date-1, 
                   pformula = ~  1, 
                   data = umf12, keyfun = "hazard", mixture = "NB", se = T)

hab.region.d12 = gdistsamp(lambdaformula = ~habtype + region - 1, 
                   phiformula = ~date-1, 
                   pformula = ~  1, 
                   data = umf12, keyfun = "hazard", mixture = "NB", se = T)

hab.dist.d12 = gdistsamp(lambdaformula = ~habtype + dista - 1, 
                   phiformula = ~date-1, 
                   pformula = ~  1, 
                   data = umf12, keyfun = "hazard", mixture = "NB", se = T)

waterd.int12 = gdistsamp(lambdaformula = ~waterd + int - 1, 
                   phiformula = ~1, 
                   pformula = ~  1, 
                   data = umf12, keyfun = "hazard", mixture = "NB", se = T)


global12 = gdistsamp(lambdaformula = ~habtype+dur+dista+region+waterd+int-1, 
                       phiformula = ~1,
                       pformula = ~ 1, 
                       data = umf12, 
                       keyfun = "hazard", 
                       mixture="NB",
                       se = T)

int12 = gdistsamp(lambdaformula = ~int-1, 
                  phiformula = ~1, 
                  pformula = ~  1,
                  data = umf12, keyfun = "hazard", mixture="NB",se = T)

waterd12 = gdistsamp(lambdaformula = ~waterd-1, 
                  phiformula = ~1, 
                  pformula = ~  1,
                  data = umf12, keyfun = "hazard", mixture="NB",se = T)
 
hab12 = gdistsamp(lambdaformula = ~habtype-1, 
                   phiformula = ~1, 
                   pformula = ~  1,
                   data = umf12, keyfun = "hazard", mixture="NB",se = T)
 
dur12 = gdistsamp(lambdaformula = ~dur-1, 
                   phiformula = ~1, 
                   pformula = ~  1,
                   data = umf12, keyfun = "hazard", mixture="NB",se = T)

region12 = gdistsamp(lambdaformula = ~region-1, 
                  phiformula = ~1, 
                  pformula = ~ 1,
                  data = umf12, keyfun = "hazard", mixture="NB",se = T)

dist12 = gdistsamp(lambdaformula = ~dista- 1, 
                  phiformula = ~1, 
                  pformula = ~  1, 
                  data = umf12, keyfun = "hazard", mixture = "NB", se = T)

hab.int12 = gdistsamp(lambdaformula = ~habtype + int - 1, 
                  phiformula = ~1, 
                  pformula = ~  1, 
                  data = umf12, keyfun = "hazard", mixture = "NB", se = T)

hab.int.waterd12 = gdistsamp(lambdaformula = ~habtype + int + waterd - 1, 
                   phiformula = ~1, 
                   pformula = ~  1, 
                   data = umf12, keyfun = "hazard", mixture = "NB", se = T)

hab.waterd12 = gdistsamp(lambdaformula = ~habtype + waterd - 1, 
                   phiformula = ~1, 
                   pformula = ~  1, 
                   data = umf12, keyfun = "hazard", mixture = "NB", se = T)

hab.dur12 = gdistsamp(lambdaformula = ~habtype + dur - 1, 
                   phiformula = ~1, 
                   pformula = ~  1, 
                   data = umf12, keyfun = "hazard", mixture = "NB", se = T)

hab.region12 = gdistsamp(lambdaformula = ~habtype + region - 1, 
                   phiformula = ~1, 
                   pformula = ~  1, 
                   data = umf12, keyfun = "hazard", mixture = "NB", se = T)

hab.dist12 = gdistsamp(lambdaformula = ~habtype + dista - 1, 
                   phiformula = ~1, 
                   pformula = ~  1, 
                   data = umf12, keyfun = "hazard", mixture = "NB", se = T)

hab.region.int12 = gdistsamp(lambdaformula = ~habtype + region + int - 1, 
                   phiformula = ~1, 
                   pformula = ~  1, 
                   data = umf12, keyfun = "hazard", mixture = "NB", se = T)
                   
list12 = fitList(null12, int12, hab.int12, hab.int.waterd12, hab.waterd12, waterd12, hab.region.int12, dist12, region12, dur12, hab12, hab.dur12,hab.region12, hab.dist12)
model12 = modSel(list12)

# 2013

#read in the sora observations
sora13 <- read.csv('2013sora.csv', header=T)
sora13 <-  sora13[,colnames(sora13)!=("impounda")]
sora13 <-  sora13[,colnames(sora13)!=("distance")]

#read in the covariate data #organized by impoundment.
cov13 <- read.csv('2013cov.csv', header=T)
#subset the covariates we need
cov13 <- cov13[,c("habtype","region","dur","dista","int","effortm","waterd")]
#the distance bins
cutpt = as.numeric(c(0,1,2,3,4,5,6,7,8,9,10,11,12)) #the fartherest distance is 12
#Unmarked Data Frame
umf13 = unmarkedFrameGDS(y=sora13, 
                           numPrimary=22,
                           siteCovs = cov13,
                           survey="line", 
                           dist.breaks=cutpt,  
                           unitsIn="m", 
                           tlength=cov13$effortm,
#                           yearlySiteCovs=list(date=date13)
)
##candidate models 
null13 = gdistsamp(lambdaformula = ~1,
                     phiformula = ~1, 
                     pformula = ~1, 
                     data = umf13, keyfun = "hazard",
                     mixture="NB",
                     se = T)
                     
global13 = gdistsamp(lambdaformula = ~habtype+dur+dista+region+waterd+int-1, 
                       phiformula = ~1,
                       pformula = ~  1, 
                       data = umf13, 
                       keyfun = "hazard",
                        mixture="NB",
                        K=200,
                       se = T)

int13 = gdistsamp(lambdaformula = ~int-1, 
                  phiformula = ~1, 
                  pformula = ~  1,
                  data = umf13, keyfun = "hazard", mixture="NB",se = T)

waterd13 = gdistsamp(lambdaformula = ~waterd-1, 
                  phiformula = ~1, 
                  pformula = ~  1,
                  data = umf13, keyfun = "hazard", mixture="NB",se = T)
 
hab13 = gdistsamp(lambdaformula = ~habtype-1, 
                   phiformula = ~1, 
                   pformula = ~  1,
                   data = umf13, keyfun = "hazard", mixture="NB",se = T)
 
dur13 = gdistsamp(lambdaformula = ~dur-1, 
                   phiformula = ~1, 
                   pformula = ~  1,
                   data = umf13, keyfun = "hazard", mixture="NB",se = T)

region13 = gdistsamp(lambdaformula = ~region-1, 
                  phiformula = ~1, 
                  pformula = ~ 1,
                  data = umf13, keyfun = "hazard", mixture="NB",se = T)

dist13 = gdistsamp(lambdaformula = ~dista- 1, 
                  phiformula = ~1, 
                  pformula = ~  1, 
                  data = umf13, keyfun = "hazard", mixture = "NB", se = T)

hab.int13 = gdistsamp(lambdaformula = ~habtype + int - 1, 
                  phiformula = ~1, 
                  pformula = ~  1, 
                  data = umf13, keyfun = "hazard", mixture = "NB", se = T)

hab.int.waterd13 = gdistsamp(lambdaformula = ~habtype + int + waterd - 1, 
                   phiformula = ~1, 
                   pformula = ~  1, 
                   data = umf13, keyfun = "hazard", mixture = "NB", se = T)

hab.waterd13 = gdistsamp(lambdaformula = ~habtype + waterd - 1, 
                   phiformula = ~1, 
                   pformula = ~  1, 
                   data = umf13, keyfun = "hazard", mixture = "NB", se = T)

hab.dur13 = gdistsamp(lambdaformula = ~habtype + dur - 1, 
                   phiformula = ~1, 
                   pformula = ~  1, 
                   data = umf13, keyfun = "hazard", mixture = "NB", se = T)

hab.region13 = gdistsamp(lambdaformula = ~habtype + region - 1, 
                   phiformula = ~1, 
                   pformula = ~  1, 
                   data = umf13, keyfun = "hazard", mixture = "NB", se = T)

hab.dist13 = gdistsamp(lambdaformula = ~habtype + dista - 1, 
                   phiformula = ~1, 
                   pformula = ~  1, 
                   data = umf13, keyfun = "hazard", mixture = "NB", se = T)

hab.region.int13 = gdistsamp(lambdaformula = ~habtype + region + int - 1, 
                   phiformula = ~1, 
                   pformula = ~  1, 
                   data = umf13, keyfun = "hazard", mixture = "NB", se = T)
                   
list13 = fitList(null13, int13, hab.int13, hab.int.waterd13, hab.waterd13, waterd13, hab.region.int13, dist13, region13, dur13, hab13, hab.dur13,hab.region13, hab.dist13)
model13 = modSel(list13)

# Output Tables from models

model12

model13


# Prediction Data Frames


phiw12i <-  data.frame(int = seq(min(cov12$int), max(cov12$int), length=15),
                      waterd = mean(cov12$waterd),
                      habtype=rep(factor(x=c("ms", "pe"), levels = c("pe", "ms")),each=15))

phiw12w <-  data.frame(int = mean(cov12$int),
                      waterd = seq(min(cov12$waterd),max(cov12$waterd),length=15),
                      habtype=rep(factor(x=c("ms", "pe"), levels = c("pe", "ms")),each=15))


pdur13 <- data.frame(dur=cov13$dur)
phiw13w <-  data.frame(int = mean(cov13$int),
                      waterd = seq(min(cov13$waterd),max(cov13$waterd),length=15),
                      habtype=rep(factor(x=c("ms", "pe"), levels = c("pe", "ms")),each=15))

phiw13i <-  data.frame(int = seq(min(cov13$int), max(cov13$int), length=15),
                      waterd = mean(cov13$waterd),
                      habtype=rep(factor(x=c("ms", "pe"), levels = c("pe", "ms")),each=15))


```
# Predictions
```{r, warning=FALSE, message=FALSE}
phiw12w <- predict(hab.int.waterd12, type="lambda",newdata=phiw12w, appendData=T)
phiw12i <-predict(hab.int.waterd12, type="lambda",newdata=phiw12i, appendData=T)
pdur13 <- predict(dur13, type="lambda", newdata=pdur13, appendData=T)
phiw13w <-predict(hab.int.waterd13, type="lambda",newdata=phiw13w, appendData=T)
phiw13i <-predict(hab.int.waterd13, type="lambda",newdata=phiw13i, appendData=T)
```

# Figure 1 - Sora Abundance by Duration 2013
```{r, fig.width=15, fig.height=15}

pdur13$durtitle = ifelse(pdur13$dur=="a","June",
                           ifelse(pdur13$dur=="b", "July",
                                  ifelse(pdur13$dur=="c","August",
                                         ifelse(pdur13$dur=="d","September",
                                                ifelse(pdur13$dur=="e","October",
                                                       ifelse(pdur13$dur=="f","After October",
                                                              ifelse(pdur13$dur=="g","Constant",NA)))))))

pdur13$durtitle = as.factor(pdur13$durtitle)
pdur13$durtitle = factor(pdur13$durtitle, levels=c("June","July", "August", "September", "October", "After October", "Constant"))


color = c("#fec44f","#fe9929","#ec7014","#cc4c02","#8c2d04")

ggplot(pdur13, aes(x=durtitle, y=Predicted, fill=durtitle),) + 
  geom_bar( position=position_dodge(), stat="identity", colour="black", size=.8)+
  geom_errorbar(aes(ymin=Predicted-SE, ymax=Predicted+SE),
                size=.3,    # Thinner lines
                width=.2,
                position=position_dodge(.9),
                colour="black") +
  xlab("Habitat Types") +
  ylab("Sora per Hectare") +
  ggtitle("Sora Density by Flood up Month in 2013") +
  scale_fill_manual(values=color)+
  theme(plot.title = element_text(colour="black",size=40), #plot title
        axis.text.x = element_text(colour="black", size=20), #x axis labels
        axis.text.y = element_text(colour="black",size=20), #y axis labels
        axis.title.x = element_text(colour="black", size=30, vjust=-.5), #x axis title
        axis.title.y = element_text(colour="black",size=30), #y axis title
        legend.text = element_blank(), #legend text
        legend.title = element_blank(),#legend title
        legend.background = element_blank(), #legend background color
        #legend.position = element_blank(),
        #legend.direction= element_blank(),
        legend.key = element_blank(),
        plot.background = element_rect(fill = "#999999" ), #plot background color
        panel.background = element_rect(fill = "#999999"), #panel background color
        panel.grid.major.y= element_line(colour="black"), #y axis grid line color
        panel.grid.major.x = element_line(colour=NA),
        panel.grid.minor = element_line(colour=NA))+ #x axis grid line color
  guides(fill=F) #retitles the legend
```
# Figure 2 - Sora Abundance by Water Depth in 2012
```{r, fig.width=15, fig.height=15}

phiw12w$habtitle = ifelse(phiw12w$habtype=="ms","Moist Soil",
                           ifelse(phiw12w$habtype=="pe", "Perennial Emergent",NA))


color = c("#fec44f","#fe9929","#ec7014","#cc4c02","#8c2d04")

ggplot() +
  geom_line(data=phiw12w, aes(x=waterd, y=Predicted, group=habtitle, colour=habtitle), size=2)+
  xlab("Water Depth (cm") +
  ylab("Sora per Hectare") +
  scale_y_continuous(limits=c(0,100))+
  #ggtitle("The Impact of Interspersion\n on Sora Density in 2012 Round 2") +
  #scale_colour_manual(values=cbPalette)+
  theme(plot.title = element_text(colour="black",size=40), #plot title
        axis.text.x = element_text(colour="black", size=20), #x axis labels
        axis.text.y = element_text(colour="black",size=20), #y axis labels
        axis.title.x = element_text(colour="black", size=30, vjust=-.5), #x axis title
        axis.title.y = element_text(colour="black",size=30), #y axis title
        legend.text = element_text(colour="black", size=20), #legend text
        legend.title = element_blank(),#legend title
        legend.background = element_rect(fill="white"), #legend background color
        legend.position = "top",
        legend.direction= "horizontal",
        legend.key = element_blank(),
        plot.background = element_rect(fill = "white" ), #plot background color
        panel.background = element_rect(fill = "white"), #panel background color
        panel.grid.major.y= element_line(colour="black"), #y axis grid line color
        panel.grid.major.x = element_line(colour=NA),
        panel.grid.minor = element_line(colour=NA),
        plot.margin = unit(c(3,3,3,3), "line"))
```
# Figure 3 - Sora Abundance by Interspersion in 2012
```{r, fig.width=15, fig.height=15}

phiw12i$habtitle = ifelse(phiw12i$habtype=="ms","Moist Soil",
                           ifelse(phiw12i$habtype=="pe", "Perennial Emergent",NA))


color = c("#fec44f","#fe9929","#ec7014","#cc4c02","#8c2d04")

ggplot() +
  geom_line(data=phiw12i, aes(x=int, y=Predicted, group=habtitle, colour=habtitle), size=2)+
  xlab("Water Depth (cm)") +
  ylab("Sora per Hectare") +
  scale_y_continuous(limits=c(0,100))+
  #ggtitle("The Impact of Interspersion\n on Sora Density in 2012 Round 2") +
  #scale_colour_manual(values=cbPalette)+
  theme(plot.title = element_text(colour="black",size=40), #plot title
        axis.text.x = element_text(colour="black", size=20), #x axis labels
        axis.text.y = element_text(colour="black",size=20), #y axis labels
        axis.title.x = element_text(colour="black", size=30, vjust=-.5), #x axis title
        axis.title.y = element_text(colour="black",size=30), #y axis title
        legend.text = element_text(colour="black", size=20), #legend text
        legend.title = element_blank(),#legend title
        legend.background = element_rect(fill="white"), #legend background color
        legend.position = "top",
        legend.direction= "horizontal",
        legend.key = element_blank(),
        plot.background = element_rect(fill = "white" ), #plot background color
        panel.background = element_rect(fill = "white"), #panel background color
        panel.grid.major.y= element_line(colour="black"), #y axis grid line color
        panel.grid.major.x = element_line(colour=NA),
        panel.grid.minor = element_line(colour=NA),
        plot.margin = unit(c(3,3,3,3), "line"))
```
# Figure 4 - Sora Abundance by Water Depth in 2013
```{r, fig.width=15, fig.height=15}
phiw13w$habtitle = ifelse(phiw13w$habtype=="ms","Moist Soil",
                           ifelse(phiw13w$habtype=="pe", "Perennial Emergent",NA))


color = c("#fec44f","#fe9929","#ec7014","#cc4c02","#8c2d04")

ggplot() +
  geom_line(data=phiw13w, aes(x=waterd, y=Predicted, group=habtitle, colour=habtitle), size=2)+
  xlab("Water Depth (cm)") +
  ylab("Sora per Hectare") +
  scale_y_continuous(limits=c(0,100))+
  #ggtitle("The Impact of Interspersion\n on Sora Density in 2012 Round 2") +
  #scale_colour_manual(values=cbPalette)+
  theme(plot.title = element_text(colour="black",size=40), #plot title
        axis.text.x = element_text(colour="black", size=20), #x axis labels
        axis.text.y = element_text(colour="black",size=20), #y axis labels
        axis.title.x = element_text(colour="black", size=30, vjust=-.5), #x axis title
        axis.title.y = element_text(colour="black",size=30), #y axis title
        legend.text = element_text(colour="black", size=20), #legend text
        legend.title = element_blank(),#legend title
        legend.background = element_rect(fill="white"), #legend background color
        legend.position = "top",
        legend.direction= "horizontal",
        legend.key = element_blank(),
        plot.background = element_rect(fill = "white" ), #plot background color
        panel.background = element_rect(fill = "white"), #panel background color
        panel.grid.major.y= element_line(colour="black"), #y axis grid line color
        panel.grid.major.x = element_line(colour=NA),
        panel.grid.minor = element_line(colour=NA),
        plot.margin = unit(c(3,3,3,3), "line"))
```
# Figure 5 - Sora Abundance by Interspersion in 2013
```{r, fig.width=15, fig.height=15}
phiw13i$habtitle = ifelse(phiw13i$habtype=="ms","Moist Soil",
                           ifelse(phiw13i$habtype=="pe", "Perennial Emergent",NA))


color = c("#fec44f","#fe9929","#ec7014","#cc4c02","#8c2d04")

ggplot() +
  geom_line(data=phiw13i, aes(x=int, y=Predicted, group=habtitle, colour=habtitle), size=2)+
  xlab("Water Depth (cm)") +
  ylab("Sora per Hectare") +
  scale_y_continuous(limits=c(0,100))+
  #ggtitle("The Impact of Interspersion\n on Sora Density in 2012 Round 2") +
  #scale_colour_manual(values=cbPalette)+
  theme(plot.title = element_text(colour="black",size=40), #plot title
        axis.text.x = element_text(colour="black", size=20), #x axis labels
        axis.text.y = element_text(colour="black",size=20), #y axis labels
        axis.title.x = element_text(colour="black", size=30, vjust=-.5), #x axis title
        axis.title.y = element_text(colour="black",size=30), #y axis title
        legend.text = element_text(colour="black", size=20), #legend text
        legend.title = element_blank(),#legend title
        legend.background = element_rect(fill="white"), #legend background color
        legend.position = "top",
        legend.direction= "horizontal",
        legend.key = element_blank(),
        plot.background = element_rect(fill = "white" ), #plot background color
        panel.background = element_rect(fill = "white"), #panel background color
        panel.grid.major.y= element_line(colour="black"), #y axis grid line color
        panel.grid.major.x = element_line(colour=NA),
        panel.grid.minor = element_line(colour=NA),
        plot.margin = unit(c(3,3,3,3), "line"))
```
