```{r}
# predictions from GDistsamp 2014
setwd("~/Documents/data")
library(unmarked)
#read in the sora observations
sora14 <- read.csv('2014_vira.csv', header=T)
#read in the covariate data #organized by impoundment.
cov14 <- read.csv('2014_cov_vira.csv', header=T)
#subset covaraites we need
cov14 <- cov14[,c("region","length","impound","jdate","area", "int","short","averagewater")]
# #the distance bins

sora14 <- sora14[order(sora14$impound),]
cov14 <- cov14[order(cov14$impound),]

sora14 <- sora14[,2:79]
cutpt = as.numeric(c(0,1,2,3,4,5,6,7,8,9,10,11,12,13)) 
#Unmarked Data Frame
umf14 = unmarkedFrameGDS(y=sora14, 
                           numPrimary=6,
                           siteCovs = cov14,
                           survey="line", 
                           dist.breaks=cutpt,  
                           unitsIn="m", 
                           tlength=cov14$length,
)
```

```{r}

model14 <- list()
model14$null14 = gdistsamp(lambdaformula = ~1, 
                     phiformula = ~1, 
                     pformula = ~1,
                     data = umf14, keyfun = "hazard", mixture="NB",se = T, output="abund")

model14$reg14 = gdistsamp(lambdaformula = ~region-1, 
                    phiformula = ~1, 
                    pformula = ~ 1,
                    data = umf14, keyfun = "hazard", mixture="NB",se = T, output="abund")
```
```{r}


model14$reg_w14 =gdistsamp(lambdaformula = ~region+averagewater-1, 
                     phiformula = ~1, 
                     pformula = ~ 1,
                     data = umf14, keyfun = "hazard", mixture="NB",se = T, output="abund")

model14$reg_w_i_14 =gdistsamp(lambdaformula = ~region+averagewater+region*averagewater-1, 
                     phiformula = ~1, 
                     pformula = ~ 1,
                     data = umf14, keyfun = "hazard", mixture="NB",se = T, output="abund")
```
```{r}
model14$short_r14 =gdistsamp(lambdaformula = ~short+region-1, 
                     phiformula = ~1, 
                     pformula = ~ 1,
                     data = umf14, keyfun = "hazard", mixture="NB",se = T, output="abund")
model14$short_r_i_14 =gdistsamp(lambdaformula = ~short+region+short*region-1, 
                     phiformula = ~1, 
                     pformula = ~ 1,
                     data = umf14, keyfun = "hazard", mixture="NB",se = T, output="abund")


```{r}
model14$short14 =gdistsamp(lambdaformula = ~short-1, 
                     phiformula = ~1, 
                     pformula = ~ 1,
                     data = umf14, keyfun = "hazard", mixture="NB",se = T, output="abund")

model14$short_w14 =gdistsamp(lambdaformula = ~short+averagewater-1, 
                       phiformula = ~1, 
                       pformula = ~ 1,
                       data = umf14, keyfun = "hazard", mixture="NB",se = T, output="abund")

model14$short_w_i_14 =gdistsamp(lambdaformula = ~short+averagewater+short*averagewater-1, 
                       phiformula = ~1, 
                       pformula = ~ 1,
                       data = umf14, keyfun = "hazard", mixture="NB",se = T, output="abund")
```
```{r}
model14$global14 =gdistsamp(lambdaformula = ~region+averagewater+short+region*averagewater+region*short-1, 
                      phiformula = ~1, 
                      pformula = ~ 1,
                      data = umf14, keyfun = "hazard", mixture="P",se = T, output="abund")

```
```{r}

list14  = fitList(model14)
model14 = modSel(list14)
model14
```