```{r}
setwd("~/GitHub/data")
# predictions from GDistsamp 2012
library(unmarked)
#read in the sora observations
sora12r1 <- read.csv('2012r1_sora.csv', header=T)
#read in the covariate data #organized by impoundment.
cov12r1 <- read.csv('2012r1_cov.csv', header=T)
#subset covaraites we need
cov12r1 <- cov12r1[,c("region","length_1","impound","jdate_1","hectares","area", "int","short","water")]
# #the distance bins

sora12r1 <- sora12r1[order(sora12r1$impound),]
cov12r1 <- cov12r1[order(cov12r1$impound),]

sora12r1 <- sora12r1[,3:15]
cutpt = as.numeric(c(0,1,2,3,4,5,6,7,8,9,10,11,12,13)) 
#Unmarked Data Frame
umf12r1 = unmarkedFrameGDS(y=sora12r1, 
                           numPrimary=1,
                           siteCovs = cov12r1,
                           survey="line", 
                           dist.breaks=cutpt,  
                           unitsIn="m", 
                           tlength=cov12r1$length_1,
)
```
```{r}

model12r1 <- list()
model12r1$null12r1 = gdistsamp(lambdaformula = ~1, 
                     phiformula = ~1, 
                     pformula = ~1,
                     data = umf12r1, keyfun = "hazard", mixture="P",se = T, output="abund")

model12r1$reg12r1 = gdistsamp(lambdaformula = ~region-1, 
                    phiformula = ~1, 
                    pformula = ~ 1,
                    data = umf12r1, keyfun = "hazard", mixture="P",se = T, output="abund")
```
```{r}


model12r1$reg_w12r1 =gdistsamp(lambdaformula = ~region+water-1, 
                     phiformula = ~1, 
                     pformula = ~ 1,
                     data = umf12r1, keyfun = "hazard", mixture="P",se = T, output="abund")

model12r1$reg_w_i_12r1 =gdistsamp(lambdaformula = ~region+water+region*water-1, 
                     phiformula = ~1, 
                     pformula = ~ 1,
                     data = umf12r1, keyfun = "hazard", mixture="P",se = T, output="abund")
```
```{r}
model12r1$short_r12r1 =gdistsamp(lambdaformula = ~short+region-1, 
                     phiformula = ~1, 
                     pformula = ~ 1,
                     data = umf12r1, keyfun = "hazard", mixture="P",se = T, output="abund")
model12r1$short_r_i_12r1 =gdistsamp(lambdaformula = ~short+region+short*region-1, 
                     phiformula = ~1, 
                     pformula = ~ 1,
                     data = umf12r1, keyfun = "hazard", mixture="P",se = T, output="abund")


```{r}
model12r1$short12r1 =gdistsamp(lambdaformula = ~short-1, 
                     phiformula = ~1, 
                     pformula = ~ 1,
                     data = umf12r1, keyfun = "hazard", mixture="P",se = T, output="abund")

model12r1$short_w12r1 =gdistsamp(lambdaformula = ~short+water-1, 
                       phiformula = ~1, 
                       pformula = ~ 1,
                       data = umf12r1, keyfun = "hazard", mixture="P",se = T, output="abund")
model12r1$short_w_i_12r1 =gdistsamp(lambdaformula = ~short+water+short*water-1, 
                       phiformula = ~1, 
                       pformula = ~ 1,
                       data = umf12r1, keyfun = "hazard", mixture="P",se = T, output="abund")
```
```{r}
model12r1$global12r1 =gdistsamp(lambdaformula = ~region+water+short+region*water+water*short+region*short+region*water*short-1, 
                      phiformula = ~1, 
                      pformula = ~ 1,
                      data = umf12r1, keyfun = "hazard", mixture="P",se = T, output="abund")

```
```{r}
list12r1  = fitList(model12r1)
model12r1 = modSel(list12r1)
model12r1
```