```{r}
# predictions from GDistsamp 2012
setwd("~/Documents/data")
library(unmarked)
#read in the sora observations
sora13 <- read.csv('2013_vira.csv', header=T)
#read in the covariate data #organized by impoundment.
cov13 <- read.csv('2013_cov_vira.csv', header=T)
#subset covaraites we need
cov13 <- cov13[,c("region","length","impound","jdate","area", "int","short","water")]
# #the distance bins

sora13 <- sora13[order(sora13$impound),]
cov13 <- cov13[order(cov13$impound),]

sora13 <- sora13[,2:79]
cutpt = as.numeric(c(0,1,2,3,4,5,6,7,8,9,10,11,12,13)) 
#Unmarked Data Frame
umf13 = unmarkedFrameGDS(y=sora13, 
                           numPrimary=6,
                           siteCovs = cov13,
                           survey="line", 
                           dist.breaks=cutpt,  
                           unitsIn="m", 
                           tlength=cov13$length,
)
```

```{r}

model13 <- list()
model13$null13 = gdistsamp(lambdaformula = ~1, 
                     phiformula = ~1, 
                     pformula = ~1,
                     data = umf13, keyfun = "hazard", mixture="NB",se = T, output="abund")

model13$reg13 = gdistsamp(lambdaformula = ~region-1, 
                    phiformula = ~1, 
                    pformula = ~ 1,
                    data = umf13, keyfun = "hazard", mixture="NB",se = T, output="abund")
```
```{r}


model13$reg_w13 =gdistsamp(lambdaformula = ~region+water-1, 
                     phiformula = ~1, 
                     pformula = ~ 1,
                     data = umf13, keyfun = "hazard", mixture="NB",se = T, output="abund")

model13$reg_w_i_13 =gdistsamp(lambdaformula = ~region+water+region*water-1, 
                     phiformula = ~1, 
                     pformula = ~ 1,
                     data = umf13, keyfun = "hazard", mixture="NB",se = T, output="abund")
```
```{r}
model13$short_r13 =gdistsamp(lambdaformula = ~short+region-1, 
                     phiformula = ~1, 
                     pformula = ~ 1,
                     data = umf13, keyfun = "hazard", mixture="NB",se = T, output="abund")
model13$short_r_i_13 =gdistsamp(lambdaformula = ~short+region+short*region-1, 
                     phiformula = ~1, 
                     pformula = ~ 1,
                     data = umf13, keyfun = "hazard", mixture="NB",se = T, output="abund")


```{r}
model13$short13 =gdistsamp(lambdaformula = ~short-1, 
                     phiformula = ~1, 
                     pformula = ~ 1,
                     data = umf13, keyfun = "hazard", mixture="NB",se = T, output="abund")

model13$short_w13 =gdistsamp(lambdaformula = ~short+water-1, 
                       phiformula = ~1, 
                       pformula = ~ 1,
                       data = umf13, keyfun = "hazard", mixture="NB",se = T, output="abund")

model13$short_w_i_13 =gdistsamp(lambdaformula = ~short+water+short*water-1, 
                       phiformula = ~1, 
                       pformula = ~ 1,
                       data = umf13, keyfun = "hazard", mixture="NB",se = T, output="abund")
```
```{r}
model13$global13 =gdistsamp(lambdaformula = ~region+water+short+region*water+region*short-1, 
                      phiformula = ~1, 
                      pformula = ~ 1,
                      data = umf13, keyfun = "hazard", mixture="NB",se = T, output="abund")

```
```{r}

list13  = fitList(model13)
model13 = modSel(list13)
model13
```