```{r}
# predictions from GDistsamp 2012
setwd("~/Documents/data")
library(unmarked)
#read in the sora observations
sora12 <- read.csv('2012_vira_occ.csv', header=T)
#read in the covariate data #organized by impoundment.
cov12 <- read.csv('2012_cov_vira.csv', header=T)
#subset covaraites we need
cov12 <- cov12[,c("region","length","impound","jdate","area", "int","short","water")]
# #the distance bins

sora12 <- sora12[order(sora12$impound),]
cov12 <- cov12[order(cov12$impound),]

sora12 <- sora12[,2:22]
cutpt = as.numeric(c(0,2,4,6,8,10,12,14)) 
#Unmarked Data Frame
umf12 = unmarkedFrameGDS(y=sora12, 
                           numPrimary=3,
                           siteCovs = cov12,
                           survey="line", 
                           dist.breaks=cutpt,  
                           unitsIn="m", 
                           tlength=cov12$length,
)
```

```{r}

model12 <- list()
model12$null12 = gdistsamp(lambdaformula = ~1, 
                     phiformula = ~1, 
                     pformula = ~1,
                     data = umf12, keyfun = "hazard", mixture="NB",se = T, output="abund")

model12$reg12 = gdistsamp(lambdaformula = ~region-1, 
                    phiformula = ~1, 
                    pformula = ~ 1,
                    data = umf12, keyfun = "hazard", mixture="NB",se = T, output="abund")
```
```{r}


model12$reg_w12 =gdistsamp(lambdaformula = ~region+water-1, 
                     phiformula = ~1, 
                     pformula = ~ 1,
                     data = umf12, keyfun = "hazard", mixture="NB",se = T, output="abund")

model12$reg_w_i_12 =gdistsamp(lambdaformula = ~region+water+region*water-1, 
                     phiformula = ~1, 
                     pformula = ~ 1,
                     data = umf12, keyfun = "hazard", mixture="NB",se = T, output="abund")
```
```{r}
model12$short_r12 =gdistsamp(lambdaformula = ~short+region-1, 
                     phiformula = ~1, 
                     pformula = ~ 1,
                     data = umf12, keyfun = "hazard", mixture="NB",se = T, output="abund")
model12$short_r_i_12 =gdistsamp(lambdaformula = ~short+region+short*region-1, 
                     phiformula = ~1, 
                     pformula = ~ 1,
                     data = umf12, keyfun = "hazard", mixture="NB",se = T, output="abund")


```{r}
model12$short12 =gdistsamp(lambdaformula = ~short-1, 
                     phiformula = ~1, 
                     pformula = ~ 1,
                     data = umf12, keyfun = "hazard", mixture="NB",se = T, output="abund")

model12$short_w12 =gdistsamp(lambdaformula = ~short+water-1, 
                       phiformula = ~1, 
                       pformula = ~ 1,
                       data = umf12, keyfun = "hazard", mixture="NB",se = T, output="abund")

model12$short_w_i_12 =gdistsamp(lambdaformula = ~short+water+short*water-1, 
                       phiformula = ~1, 
                       pformula = ~ 1,
                       data = umf12, keyfun = "hazard", mixture="NB",se = T, output="abund")
```
```{r}
model12$global12 =gdistsamp(lambdaformula = ~region+water+short+region*water+region*short-1, 
                      phiformula = ~1, 
                      pformula = ~ 1,
                      data = umf12, keyfun = "hazard", mixture="P",se = T, output="abund")

```
```{r}

list12  = fitList(model12)
model12 = modSel(list12)
model12
```