```{r}
# predictions from GDistsamp 2013

library(unmarked)
#read in the sora observations
sora13 <- read.csv('./data/2013_vira_occ.csv', header=T)
#read in the covariate data #organized by impoundment.
cov13 <- read.csv('./data/2013_cov_vira.csv', header=T)
#subset covaraites we need
cov13 <- cov13[,c("region","length","impound","jdate","area", "int","short","water")]
# #the distance bins

sora13 <- sora13[order(sora13$impound),]
cov13 <- cov13[order(cov13$impound),]

sora13 <- sora13[,2:22]
cutpt = as.numeric(c(0,2,4,6,8,10,13,14)) 
#Unmarked Data Frame
umf13 = unmarkedMultFrame(y=sora13, 
                           numPrimary=3,
                           siteCovs = cov13,
)
```

```{r}

model13 <- list()
model13$null13 = colext(psiformula= ~1, gammaformula = ~ 1, epsilonformula = ~ 1, pformula = ~ 1, data = umf13, method="BFGS")


model13$reg13 = colext(psiformula= ~region-1, gammaformula = ~ 1, epsilonformula = ~ 1, pformula = ~ 1, data = umf13, method="BFGS")
```
```{r}


model13$reg_w13 =colext(psiformula= ~region+water-1, gammaformula = ~ 1, epsilonformula = ~ 1, pformula = ~ 1, data = umf13, method="BFGS")

model13$reg_w_i_13 =colext(psiformula= ~region+water+region*water-1, gammaformula = ~ 1, epsilonformula = ~ 1, pformula = ~ 1, data = umf13, method="BFGS")

  
```
```{r}
model13$short_r13 =colext(psiformula= ~short+region-1, gammaformula = ~ 1, epsilonformula = ~ 1, pformula = ~ 1, data = umf13, method="BFGS")

model13$short_r_i_13 =colext(psiformula= ~short+region+short*region-1, gammaformula = ~ 1, epsilonformula = ~ 1, pformula = ~ 1, data = umf13, method="BFGS")


```{r}
model13$short13 =colext(psiformula= ~short-1, gammaformula = ~ 1, epsilonformula = ~ 1, pformula = ~ 1, data = umf13, method="BFGS")

model13$short_w13 =colext(psiformula= ~short+water-1, gammaformula = ~ 1, epsilonformula = ~ 1, pformula = ~ 1, data = umf13, method="BFGS")

model13$short_w_i_13 =colext(psiformula= ~short+water+short*water-1, gammaformula = ~ 1, epsilonformula = ~ 1, pformula = ~ 1, data = umf13, method="BFGS")
```
```{r}
model13$global13 =colext(psiformula= ~region+water+short+short*region+region*water-1, gammaformula = ~ 1, epsilonformula = ~ 1, pformula = ~ 1, data = umf13, method="BFGS")

```
```{r}

list13  = fitList(model13)
model13 = modSel(list13)
model13
```