```{r}
# predictions from GDistsamp 2012
setwd("~/data")
library(unmarked)
#read in the sora observations
sora12 <- read.csv('2012_vira_occ.csv', header=T)

sora12$occu <- rowSums(sora12[,2:22])

sora12[sora12$occu>=1,]$occu <- 1

#read in the covariate data #organized by impoundment.
cov12 <- read.csv('2012_cov_vira.csv', header=T)
#subset covaraites we need
cov12 <- cov12[,c("region","length","impound","jdate","area", "int","short","water")]
# #the distance bins

sora12 <- sora12[order(sora12$impound),]
cov12 <- cov12[order(cov12$impound),]

cutpt = as.numeric(c(0,2,4,6,8,10,12,14)) 


#Unmarked Data Frame
umf12 = unmarkedFrameOccu(y=as.data.frame(sora12$occu),
                           siteCovs = cov12,
)
```

```{r}



model12 <- list()
model12$null12 = occu(~1~1,data=umf12)

model12$reg12 = colext(psiformula= ~region-1, gammaformula = ~ 1, epsilonformula = ~ 1, pformula = ~ 1, data = umf12, method="BFGS")
```
```{r}


model12$reg_w12 =colext(psiformula= ~region+water-1, gammaformula = ~ 1, epsilonformula = ~ 1, pformula = ~ 1, data = umf12, method="BFGS")

model12$reg_w_i_12 =colext(psiformula= ~region+water+region*water-1, gammaformula = ~ 1, epsilonformula = ~ 1, pformula = ~ 1, data = umf12, method="BFGS")

  
```
```{r}
model12$short_r12 =colext(psiformula= ~short+region-1, gammaformula = ~ 1, epsilonformula = ~ 1, pformula = ~ 1, data = umf12, method="BFGS")

model12$short_r_i_12 =colext(psiformula= ~short+region+short*region-1, gammaformula = ~ 1, epsilonformula = ~ 1, pformula = ~ 1, data = umf12, method="BFGS")


```{r}
model12$short12 =colext(psiformula= ~short-1, gammaformula = ~ 1, epsilonformula = ~ 1, pformula = ~ 1, data = umf12, method="BFGS")

model12$short_w12 =colext(psiformula= ~short+water-1, gammaformula = ~ 1, epsilonformula = ~ 1, pformula = ~ 1, data = umf12, method="BFGS")

model12$short_w_i_12 =colext(psiformula= ~short+water+short*water-1, gammaformula = ~ 1, epsilonformula = ~ 1, pformula = ~ 1, data = umf12, method="BFGS")
```
```{r}
model12$global12 =colext(psiformula= ~region+water+short+short*region+region*water-1, gammaformula = ~ 1, epsilonformula = ~ 1, pformula = ~ 1, data = umf12, method="BFGS")

```
```{r}

list12  = fitList(model12)
model12 = modSel(list12)
model12
```