```{r}
# predictions from GDistsamp 2014
setwd("~/Documents/data")
library(unmarked)
#read in the sora observations
sora14 <- read.csv('2014_vira_occ.csv', header=T)
#read in the covariate data #organized by impoundment.
cov14 <- read.csv('2014_cov_vira.csv', header=T)
#subset covaraites we need
cov14 <- cov14[,c("region","length","impound","jdate","area", "int","short","averagewater")]
# #the distance bins

sora14 <- sora14[order(sora14$impound),]
cov14 <- cov14[order(cov14$impound),]

sora14 <- sora14[,2:22]
cutpt = as.numeric(c(0,2,4,6,8,10,14,14)) 
#Unmarked Data Frame
umf14 = unmarkedMultFrame(y=sora14, 
                           numPrimary=3,
                           siteCovs = cov14,
)
```

```{r}

model14 <- list()
model14$null14 = colext(psiformula= ~1, gammaformula = ~ 1, epsilonformula = ~ 1, pformula = ~ 1, data = umf14, method="BFGS")


model14$reg14 = colext(psiformula= ~region-1, gammaformula = ~ 1, epsilonformula = ~ 1, pformula = ~ 1, data = umf14, method="BFGS")
```
```{r}


model14$reg_w14 =colext(psiformula= ~region+averagewater-1, gammaformula = ~ 1, epsilonformula = ~ 1, pformula = ~ 1, data = umf14, method="BFGS")

model14$reg_w_i_14 =colext(psiformula= ~region+averagewater+region*averagewater-1, gammaformula = ~ 1, epsilonformula = ~ 1, pformula = ~ 1, data = umf14, method="BFGS")

  
```
```{r}
model14$short_r14 =colext(psiformula= ~short+region-1, gammaformula = ~ 1, epsilonformula = ~ 1, pformula = ~ 1, data = umf14, method="BFGS")

model14$short_r_i_14 =colext(psiformula= ~short+region+short*region-1, gammaformula = ~ 1, epsilonformula = ~ 1, pformula = ~ 1, data = umf14, method="BFGS")


```{r}
model14$short14 =colext(psiformula= ~short-1, gammaformula = ~ 1, epsilonformula = ~ 1, pformula = ~ 1, data = umf14, method="BFGS")

model14$short_w14 =colext(psiformula= ~short+averagewater-1, gammaformula = ~ 1, epsilonformula = ~ 1, pformula = ~ 1, data = umf14, method="BFGS")

model14$short_w_i_14 =colext(psiformula= ~short+averagewater+short*averagewater-1, gammaformula = ~ 1, epsilonformula = ~ 1, pformula = ~ 1, data = umf14, method="BFGS")
```
```{r}
model14$global14 =colext(psiformula= ~region+averagewater+short+short*region+region*averagewater-1, gammaformula = ~ 1, epsilonformula = ~ 1, pformula = ~ 1, data = umf14, method="BFGS")

```
```{r}

list14  = fitList(model14)
model14 = modSel(list14)
model14
```